Embedded Scalars: {A}n Experimental Revisit

### 2014-05-29 text/paper/paper4.tex
Bayesian model revision, simpler presentation of raw results

In the following, we will report the results for targets and
preference-related controls separately. After providing the
descriptive results, we present statistical analyses using log-linear
models (i.e., generalized linear regression for count data). To
complement the picture, we also report a Bayesian analysis that probes
specifically into the preference relations between candidate readings.

@@

The answers obtained for the four target conditions are depicted in
Figure \ref{fig:JudgmentsK2}.
%
\begin{figure}[t]
\centering

\includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}

\caption{Answers for the \as- and \es-sequences. Bars show the total
  number of \emph{yes} (up) and \emph{no} judgments (down) collected
  at each step during a sequence. E.g., we recorded a total of 103
  \emph{yes} judgments at the third position in the \as-sequence with
  neutral intonation, which corresponds to 103 answers that were
  classified as \emph{literal} answers. Notice that the \as-condition
  had seven steps, the \es-condition only five.}
\label{fig:JudgmentsK2}
\end{figure}
%
We coded these answers as {\it literal}, {\it global} or {\it local}
if they were as expected under one of these readings and as {\it
  error} if not. The distribution of readings thus coded is given in
Table~\ref{tab:CC-ContingencyTable}. The table also classifies
responses according to the position (1--3) in the experiment, i.e.,
whether it was the first, second or third time that a participant saw
the critical condition in question.
%
\begin{table}[h]
\centering

\begin{tabular}{lccccc}
  condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
  && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
  \midrule \addlinespace[0.15cm]
  \textbf{\as neutral} 
  & Pos 1 & 35 &  0 & 0 & 3 \\
  & Pos 2 & 35 &  1 & 0 & 2 \\
  & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
  \textbf{8} \\
  \addlinespace[0.25cm]
  \textbf{\as accented} 
  & Pos 1 & 33 &  2 & 1 & 2 \\
  & Pos 2 & 33 &  3 & 1 & 1 \\
  & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
  \textbf{5} \\
  \addlinespace[0.25cm]
  \textbf{\es neutral} 
  & Pos 1 & 26 &  5 & 0 & 7 \\
  & Pos 2 & 26 &  3 & 0 & 9 \\
  & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
  \textbf{22} \\
  \addlinespace[0.25cm]
  \textbf{\es accented} 
  & Pos 1 & 26 &  6 & 0 & 6 \\
  & Pos 2 & 24 &  5 & 0 & 9 \\
  & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
  \textbf{20}
\end{tabular}

\caption{Contingency table of classified responses for the critical
  conditions. The factor position encodes whether participants saw the
  condition in question for the first, second or third time during the
  whole experiment.}
\label{tab:CC-ContingencyTable}
\end{table}
%
The majority of answers are indicative of a literal reading (90.35\% /
86.84\% in neutral / accented \as-conditions, and 68.42\% in both
neutral / accented \es-conditions). Only two answers across all
critical conditions fall into the category indicative of global
readings. Judgements indicative of local readings, on the other hand,
are more frequent (2.63\% / 7.02\% for neutral / accented
\as-conditions, and 12.28\% / 14.04\% for neutral / accented
\es-conditions).

The number of responses that fell out of our classification scheme
differs substantially between \as- and \es-conditions. There are
7.02\% / 4.39\% unclassifiable judgements in the neutral / accented
\as-conditions, but 19.30\% / 17.54\% in the neutral / accented
\es-conditions. A look at Figure~\ref{fig:JudgmentsK2} reveals that
there is some systematicity in 'error' answers. Most answers that we
classified as 'errors' are plausibly explained as a few random errors,
a handful of mistakes resulting from confusing buttons for \emph{true}
and \emph{false} and a few 'spill-overs' where participants gave
responses one position too late. There is one notable exception,
though. A substantial number of \emph{true} responses where given at
the second position of \es-sequences (9.65\% / 8.77\%) which is shown
in Figure~\ref{fig:exseqES2}. Although this position in the sequence
is the critical position to reveal a global reading, the latter would
be indicated by a \emph{false} response. It appears that subjects read
\es-sentences as if the non-monotonic quantifier \emph{exactly one}
was a monotonic \emph{at least one}, without pragmatic enrichment of
\emph{some}.\fn{If \emph{some} is pragmatically strengthened under the
  scope of \emph{at least one}, we would expect \emph{true} judgements
  at position 3. Although exactly 3 \emph{true} answers occurred there
  for each neutral and accented \es-conditions, the main point to
  notice is that this misreading of the non-monotonic quantifier does
  not explain \emph{true} judgements at position 5. These are
  therefore still indicative of local readings.} 16 out of the total
21 answers in this category come from 5 subjects, while the remaining
5 were single answers by 5 different subjects. \todo{subjects 1, 9,
  12, 21, 84} This suggests that at least for some subjects
non-monotonic quantifiers were problematic. \todo{how to deal with
  this in the future?}

We fitted generalized linear models to the contingency table data in
Table~\ref{tab:CC-ContingencyTable}, using factors \textsc{Condition}
with levels \as and \es, \textsc{Accent} with levels \emph{neutral}
and \emph{accented}, and \textsc{Position} with levels 1 through 3 to
predict the dependent factor \textsc{Reading} with levels
\emph{literal}, \emph{local}, and \emph{other}. The latter lumps
\emph{global} and \emph{error} responses together, because otherwise
we would not have enough cell counts to apply log-linear
regression. We selected the ``best'' predictor of the data by a
gradient search over hierarchical models in terms of AICs, starting
from the saturated model. The best model takes main factors
\textsc{Response} and \textsc{Condition} into account, as well as the
interaction term \textsc{Response:Condition} ($\chi^2 = 17.19$,
$df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$ of the
saturated model)). Crucially, factors \textsc{Position} and
\textsc{Accent} are spurious in the best model. This suggests that
response patterns only depend on the type of the sentence, but that
there were no learning or fatigation effects and that accentuation did
not influence answer patterns significantly.

\begin{table}
  \centering
  \begin{tabular}{lllll}
    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
    \midrule
    \textsc{Intercept} & 0.916  &  0.258 &  3.49  & < 0.001 \\
    \textsc{Reading}.\emph{literal} & 2.600 &   0.268 & 9.716 & < 0.001 \\
    \textsc{Reading}.\emph{local} & -0.310  &  0.397 & -0.781 &
    0.435 \\
    \textsc{Condition}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -1.288 &
    0.319 & -4.036 &  < 0.001 \\
    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & -0.026 &
    0.463 &  -0.0579 &  0.955
  \end{tabular}
  \caption{Coefficients of the ``best'' log-linear model for the count
    data in Table~\ref{tab:CC-ContingencyTable}. Notice that factor
    levels \emph{local} do not cause a significant shift in counts,
    given reference level
    \emph{false}.}
  \label{tab:Coefficients-CC}
\end{table}

Inspection of the coefficients of the ``best'' model suggests that the
distinction between levels \emph{local} and \emph{other} in factor
\textsc{Reading} might not be necessary (see
Table~\ref{tab:Coefficients-CC}). In order to test whether there is
support for the postulation of local readings, we therefore compared
the previous ``best'' predictor to a model that only differs from the
former in that it subsumes the level \emph{local} of factor
\textsc{Reading} under level \emph{other} as well
\citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model comparison
reveals that there is no significant improvement in explanatory power
($Pr(|\chi|) = 0.2689$) of the more complex model that includes the
level \emph{local} (residual df=30, residual deviance = 10.497) over the simpler
model without this level (residual df=32, residual deviance = 13.124,
AIC=157.268).

This latter analysis suggests that our data does not provide strong
evidence for the maintenance of belief in local readings in our
setting. But we need to be careful. The regression analysis tells us
that the number of errors and the number of local readings were
similar in all conditions. But the distribution of answers in
Figure~\ref{fig:JudgmentsK2} shows that small error counts occur at
many different steps, whereas we do see a concentrated rise in answers
at the critical position for local readings. Also, so far we have not
taken into account the sequential structure of our task. It might be
that local readings are infrequent because subjects tend to exit early
in the sequence, rather than late. This is why we need
preference-related controls and a more fine-grained analysis
eventually.

\paragraph{Preference-related controls.} Positional answers for our
preference-related control conditions are shown in
Figure~\ref{Fig:TF_judgments}.\fn{We removed 19 data points for the
  \ec-conditions because of a coding mistake that presented subjects
  with incongruent sentence-picture pairs. Including these and
  classifying them as \emph{errors} does not change the qualitative
  results of the reported analyses.}
%
\begin{figure}[]
\centering

 \subfloat[][\LC-sequence]{

\includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
}

 \subfloat[][\EC-sequence]{

\includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
}

\caption{Answers for \lc-sequences and \ec-sequences. \emph{True}
  judgements are plotted upwards for each step in the sequence,
  \emph{false} judgements downwards.}
\label{Fig:TF_judgments}
\end{figure}
%
Judgments were coded as \ec or as \lc if they were as expected under
one of these readings, and as \emph{error} if they were not. The
distributions of readings thus coded is given in
Table~\ref{tab:CC-ContingencyTable-TF}. Some subjects saw 4 trials of
some target-related control conditions, but the table and the
subsequent analysis of the count data only looks at the data from the
first three encounters. This is because otherwise we would see a
spurious main effect of \textsc{Position} that is just needed to
account for the less frequent occurrence of judgements at position 4.
%
\begin{table}[]
\centering

\begin{tabular}{lcccc}
  condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
  && \emph{LC} & \emph{EC} & \emph{error}  \\
  \midrule \addlinespace[0.15cm]
  \textbf{\lc neutral} 
  & Pos 1 & 27 &  7  & 4 \\
  & Pos 2 & 23 &  11 & 4 \\
  & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{11}  \\
  \addlinespace[0.25cm]
  \textbf{\lc with \lc cue} 
  & Pos 1 & 26 &  7 & 5  \\
  & Pos 2 & 31 &  5 & 2  \\
  & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{90} &  \textbf{15} & \textbf{9}  \\
  \addlinespace[0.25cm]
  \textbf{\lc with \ec cue} 
  & Pos 1 & 14 &  17 & 7  \\
  & Pos 2 & 15 &  16 & 7  \\
  & Pos 3 & 15 &  17 & 6  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{44} &  \textbf{50} & \textbf{20}  \\
  \addlinespace[0.25cm]
  \textbf{\ec neutral} 
  & Pos 1 & 22 &  6 & 5  \\
  & Pos 2 & 28 &  6 & 4  \\
  & Pos 3 & 29 &  7 & 2  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{79} &  \textbf{19} & \textbf{11}  \\
  \addlinespace[0.25cm]
  \textbf{\ec with \lc cue} 
  & Pos 1 & 30 &  5 & 1  \\
  & Pos 2 & 32 &  5 & 0  \\
  & Pos 3 & 31 &  3 & 2  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{93} &  \textbf{13} & \textbf{3}  \\
  \addlinespace[0.25cm]
  \textbf{\ec with \ec cue} 
  & Pos 1 & 19 &  10 & 7  \\
  & Pos 2 & 19 &  7  & 9  \\
  & Pos 3 & 19 &  7  & 11  \\ \addlinespace[0.15cm]
  & \textbf{Total} & \textbf{57} &  \textbf{24} & \textbf{27}  \\
\end{tabular}

\caption{Contingency table of classified responses for the
  preference-related controls. As before, the factor position encodes
  whether participants saw the condition in question for the first,
  second or third time during the whole experiment.}
\label{tab:CC-ContingencyTable-TF}
\end{table}

As expected, most answers classify as \lc-readings, fewer as
\ec-readings. Moreover, intonation does seem to have the expected
effect as well: as compared to neutral intonation, \lc-cueing
intonation increases the count for \lc-readings, while \ec-cueing
increases the count for \ec-readings. If we compare the number of \lc-
or \ec-readings for each intonation type across sequences, we see that
there are always more answers indicative of the relevant readings when
that reading can be judged later in the sequence. This suggests a
general tendency to answer later in the sequence, rather than at the
earliest possible step.

There are only very few answers that appear to be random
mistakes. Some answers in the `error' category are plausibly
`spill-over errors', where participants gave answers one step too
late. But on top of that, a substantial number of `error' answers
occurs on critical positions. For example, in the \lc-sequence there
are 23 \emph{true} answers at step 6 where \emph{false} answers would
be taken as indicative of \ec-readings. In the \ec-sequence there are
28 \emph{false} answers at step 5 where \emph{true} answers would be
taken as indicative of \lc-readings.\fn{A general tendency to answer
  later in the sequence would explain this. The reason why we do not
  see a similar effect in the critical conditions, might be because
  the literal reading is so dominant.} Finally, intonation patterns
that cue \ec-readings seem to have led to more mistakes than other
intonation patterns.

As for the critical conditions, we compute logistic regression models
including factors \textsc{Reading} with levels \lc, \ec and
\emph{error}, \textsc{Accent} with levels \emph{neutral},
\emph{\lc-cue} and \emph{\ec-cue}, \textsc{Position} with levels 1 to
3, and \textsc{Condition} with levels \lc and \ec for the picture
sequences. Starting search from the saturated model along a gradient
of decreasing AICs, we find that the ``best'' predictor relies on main
effects of \textsc{Reading}, \textsc{Accent} and \textsc{Condition}
and two two-way interactions \textsc{Response:Condition} and
\textsc{Response:Accent} ($\chi^2=18.34$, $df=42$, $p=0.99$,
$AIC=256.63$ (compared to $AIC=322.3$ of the saturated model)). Factor
\textsc{Position} again turned out to be spurious, suggesting that
answer patterns are stable over the duration of the experiment. Unlike
for the critical conditions, factor \textsc{Accent} is retained, and
it interacts with \textsc{Reading}, suggesting that intonational cues
significantly influenced the dominant reading.

\begin{table}
  \centering
  \begin{tabular}{lllll}
    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
    \midrule
    \textsc{Intercept} & 2.119  &   0.162 & 13.079   & < 0.001 \\
    \textsc{Reading}.\emph{error} & -0.343 &  0.259 & -1.328 &  0.184
    \\
    \textsc{Reading}.\lc & 0.526 &  0.202 & 2.607 & < 0.01 \\
    \textsc{Condition}.\lc & 0.497 &  0.170  & 2.929 & < 0.01 \\
    \textsc{Accent}.\lc & -1.054 & 0.242 & -4.354 & < 0.001 \\
    \textsc{Accent}.\emph{neutral} & -0.112 & 0.180 &  -0.626 &  0.531
    \\
    \textsc{Reading}.\emph{error}:\textsc{Condition}.\lc & -0.521 &
    0.280 & -1.87 & 0.062 \\
    \textsc{Reading}.\lc:\textsc{Condition}.\lc & -0.583 & 0.195 &
    -2.997 &  < 0.01 \\
    \textsc{Reading}.\emph{error}:\textsc{Accent}.\lc & -0.103 &
    0.422 &  -0.245 & 0.807  \\
    \textsc{Reading}.\lc:\textsc{Accent}.\lc & 1.657 &  0.279 & 5.943
    & < 0.001 \\
    \textsc{Reading}.\emph{error}:\textsc{Accent}.\emph{neutral} & 0.112 &
    0.299  &  0.375 &  0.708 \\
    \textsc{Reading}.\lc:\textsc{Accent}.\emph{neutral} & 1.065  &
    0.222 &  4.800 & < 0.001 \\
  \end{tabular}
  \caption{Coefficients of the ``best'' log-linear model for the count
    data in Table~\ref{tab:CC-ContingencyTable-TF}.}
  \label{tab:Coefficients-TF}
\end{table}

Closer examination of the coefficients of the fitted model, shown in
Table~\ref{tab:Coefficients-TF}, reveals that there were significantly
more \ec-readings in the \lc-condition and vice versa. This is evident
from the significant \emph{negative} deviation from the baseline of
\ec-readings in the interaction coefficient for
\textsc{Reading}.\lc:\textsc{Condition}.\lc. The log-linear model
therefore suggests that there is a bias for late responses in a
sequence. If such a preference for late responses holds for critical
conditions as well, then the marginal numer of local responses that we
observed is more likely overemphasized by our sequential decision task
than that it is underemphasized. The following Bayesian analysis
further probes into this matter in order to establish how strongly the
sequence-effect might have emphasized local readings and, from there,
whether we should uphold belief in local readings.

>>>>

In the following, we will report the results for targets and
preference-related controls separately. After providing the
descriptive results, we present statistical analyses using log-linear
models. We complement these with a Bayesian analysis that is sensitive
to the sequential nature of the incremental verification task and
probes specifically into the preference relations between candidate
readings.

@@

% \begin{figure}[t] 
% \centering

% \includegraphics[width=0.9\textwidth]{positional_answers_critical.pdf}

% \caption{Answers for the \as- and \es-sequences. Bars show the total
%   number of \emph{yes} (up) and \emph{no} judgments (down) collected
%   at each step during a sequence. E.g., we recorded a total of 103
%   \emph{yes} judgments at the third position in the \as-sequence with
%   neutral intonation, which corresponds to 103 answers that were
%   classified as \emph{literal} answers. Notice that the \as-condition
%   had seven steps, the \es-condition only five.}
% \label{fig:JudgmentsK2}
% \end{figure}
%

\begin{table}
  \centering
  \begin{tabular}{lcccccccc@{\hskip 0.6cm}cccc}
    && \multicolumn{7}{c}{truth value at step}
    & \multicolumn{4}{c}{classification}
    \\ \cmidrule(l){3-9} \cmidrule(r){10-13}
    condition &
    & 1
    & 2
    & 3
    & 4
    & 5
    & 6
    & 7
    & \lit
    & \loc
    & \glb
    & err \\ \midrule
    \as-ntr 
    & T & 1 & 1 & \textbf{103} & 2 & \textbf{0} & 0 & 2 
    & 103 & 3 & 0 & 8 \\
    & F & 0 & 0 & 0 & 0 & 2 & 0 & \textbf{3} \\ 
    \addlinespace[0.25cm]
    \as-acc
    & T & 0 & 1 & \textbf{99} & 2 & \textbf{2} & 0 & 1 
    & 99 & 8 & 5 & 5 \\
    & F & 0 & 0 & 1 & 0 & 0 & 0 & \textbf{8} \\
    \addlinespace[0.25cm]
    \es-ntr
    & T & 0 & 11 & 3 & 1 & \textbf{14} & - & - 
    & 78 & 14 & 0 & 22 \\
    & F & 0 & \textbf{0} & \textbf{78} & 5 & 2 & - & - \\
    \addlinespace[0.25cm]
    \es-acc
    & T & 0 & 10 & 3 & 0 & \textbf{16} & - & - 
    & 78 & 16 & 0 & 20 \\
    & F & 0 & \textbf{0} & \textbf{78} & 5 & 2 & - & -
  \end{tabular}
  \caption{Observed truth-value judgments in critical conditions. The
    left-hand part of the table shows the number of \emph{true} and
    \emph{false} responses obtained at each step in the sequence. The
    right-hand part shows the count for our imposed classification
    scheme. The answer counts indicative of relevant readings are
    given in bold-face on the left-hand side.}
  \label{tab:count_data_CC}
\end{table}

%
% \begin{table}[h]
% \centering

% \begin{tabular}{lccccc}
%   condition & position & \multicolumn{4}{c}{response type} \\ \cmidrule(r){3-6}
%   && \emph{literal} & \emph{local} & \emph{global} & \emph{error} \\
%   \midrule \addlinespace[0.15cm]
%   \textbf{\as neutral} 
%   & Pos 1 & 35 &  0 & 0 & 3 \\
%   & Pos 2 & 35 &  1 & 0 & 2 \\
%   & Pos 3 & 33 &  2 & 0 & 3 \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{103} &  \textbf{3} & \textbf{0} &
%   \textbf{8} \\
%   \addlinespace[0.25cm]
%   \textbf{\as accented} 
%   & Pos 1 & 33 &  2 & 1 & 2 \\
%   & Pos 2 & 33 &  3 & 1 & 1 \\
%   & Pos 3 & 33 &  3 & 0 & 2 \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{99} &  \textbf{8} & \textbf{2} &
%   \textbf{5} \\
%   \addlinespace[0.25cm]
%   \textbf{\es neutral} 
%   & Pos 1 & 26 &  5 & 0 & 7 \\
%   & Pos 2 & 26 &  3 & 0 & 9 \\
%   & Pos 3 & 26 &  6 & 0 & 6 \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{78} &  \textbf{14} & \textbf{0} &
%   \textbf{22} \\
%   \addlinespace[0.25cm]
%   \textbf{\es accented} 
%   & Pos 1 & 26 &  6 & 0 & 6 \\
%   & Pos 2 & 24 &  5 & 0 & 9 \\
%   & Pos 3 & 28 &  5 & 0 & 5 \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{78} &  \textbf{16} & \textbf{0} &
%   \textbf{20}
% \end{tabular}

% \caption{Contingency table of classified responses for the critical
%   conditions. The factor position encodes whether participants saw the
%   condition in question for the first, second or third time during the
%   whole experiment.}
% \label{tab:CC-ContingencyTable}
% \end{table}
%

Judgements obtained for the four target conditions are listed in
Table~\ref{tab:count_data_CC}. We coded these answers as {\it
  literal}, {\it global} or {\it local} if they were as expected under
one of these readings and as {\it error} if not. The majority of
answers are indicative of a literal reading (90.35\% / 86.84\% in
neutral / accented \as-conditions, and 68.42\% in both neutral /
accented \es-conditions). Only two answers across all critical
conditions fall into the category indicative of global
readings. Judgements indicative of local readings, on the other hand,
are more frequent (2.63\% / 7.02\% for neutral / accented
\as-conditions, and 12.28\% / 14.04\% for neutral / accented
\es-conditions).

The number of responses that fell out of our classification scheme
differs substantially between \as- and \es-conditions. There are
7.02\% / 4.39\% unclassifiable judgements in the neutral / accented
\as-conditions, but 19.30\% / 17.54\% in the neutral / accented
\es-conditions. A look at the right-hand side of
Table~\ref{tab:count_data_CC} reveals that there is some systematicity
in 'error' answers. Most answers that we classified as 'errors' are
plausibly explained as a few random errors, a handful of mistakes
resulting from confusing buttons for \emph{true} and \emph{false} and
a few 'spill-over errors' where participants gave responses one
position too late. There is one notable exception, though. A
substantial number of \emph{true} responses where given at the second
position of \es-sequences (9.65\% / 8.77\%) which is shown in
Figure~\ref{fig:exseqES2}. Although this position in the sequence is
the critical position to reveal a global reading, the latter would be
indicated by a \emph{false} response. It appears that subjects read
\es-sentences as if the non-monotonic quantifier \emph{exactly one}
was a monotonic \emph{at least one}, without pragmatic enrichment of
\emph{some}.\fn{If \emph{some} is pragmatically strengthened under the
  scope of \emph{at least one}, we would expect \emph{true} judgements
  at position 3. Although exactly 3 \emph{true} answers occurred there
  for each neutral and accented \es-conditions, the main point to
  notice is that this misreading of the non-monotonic quantifier does
  not explain \emph{true} judgements at position 5. These are
  therefore still indicative of local readings.} 16 out of the total
21 answers in this category come from 5 subjects, while the remaining
5 were single answers by 5 different subjects.
% subjects 1, 9, 12, 21, 84
This suggests that at least for some subjects non-monotonic
quantifiers were problematic. (We will come back to this point later.)

We fitted generalized linear models to the count data in
Table~\ref{tab:count_data_CC}, using factors \textsc{Condition} with
levels \as and \es, \textsc{Accent} with levels \emph{neutral} and
\emph{accented}, and \textsc{Position} with levels 1 through 3 (coding
whether it was the first, second or third time that a participant saw
a critical condition during the experiment) to predict the dependent
factor \textsc{Reading} with levels \emph{literal}, \emph{local}, and
\emph{other}. The latter lumps \emph{global} and \emph{error}
responses together, because otherwise we would not have enough cell
counts to apply log-linear regression. We determined the ``best''
predictor of the data by a gradient search over hierarchical models in
terms of AICs, starting from the saturated model. The best model takes
main factors \textsc{Response} and \textsc{Condition} into account, as
well as the interaction term \textsc{Response:Condition} ($\chi^2 =
17.19$, $df=42$, $p = 0.99$, $AIC = 158.01$ (compared to $AIC=208.25$
of the saturated model)). Crucially, factors \textsc{Position} and
\textsc{Accent} are spurious in the best model. This suggests that
response patterns only depend on the type of the sentence, but that
there were no learning or fatigation effects and that accentuation did
not influence answer patterns significantly (at this level of
abstraction).

\begin{table}
  \centering
  \begin{tabular}{lllll}
    coefficient & estimate & std.~error & $z$-value & $\Pr(>|z|)$ \\
    \midrule
    \textsc{Intercept} & 0.916  &  0.258 &  3.49  & < 0.001 \\
    \textsc{Reading}.\emph{literal} & 2.600 &   0.268 & 9.716 & < 0.001 \\
    \textsc{Reading}.\emph{local} & -0.310  &  0.397 & -0.781 &
    0.435 \\
    \textsc{Condition}.\es & 1.030 &  0.301 & 3.423 &  < 0.001 \\
    \textsc{Reading}.\emph{literal}:\textsc{Condition}.\es & -1.288 &
    0.319 & -4.036 &  < 0.001 \\
    \textsc{Reading}.\emph{local}:\textsc{Condition}.\es & -0.026 &
    0.463 &  -0.0579 &  0.955
  \end{tabular}
  \caption{Coefficients of the ``best'' log-linear model for the count
    data in Table~\ref{tab:count_data_CC}.}
  \label{tab:Coefficients-CC}
\end{table}

Inspection of the coefficients of the ``best'' model in
Table~\ref{tab:Coefficients-CC} suggests that the distinction between
levels \emph{local} and \emph{other} in factor \textsc{Reading} might
not be necessary: factor levels \emph{local} do not cause a
significant shift in counts, given reference level \emph{false}. In
order to test whether there is support for the postulation of local
readings, we therefore compared the previous ``best'' predictor to a
model that only differs from the former in that it subsumes the level
\emph{local} of factor \textsc{Reading} under level \emph{other} as
well \citep[e.g.][Chapter~15]{Crawley2007:The-R-Book}. Model
comparison reveals that there is no significant improvement in
explanatory power ($Pr(|\chi|) = 0.2689$) of the more complex model
that includes the level \emph{local} (residual df=30, residual
deviance = 10.497) over the simpler model without this level (residual
df=32, residual deviance = 13.124, AIC=157.268).

This latter analysis suggests that our data does not provide strong
evidence for the maintenance of belief in local readings in our
setting. But we need to be careful. The regression analysis tells us
that the number of errors and the number of local readings were
similar in all conditions. But the distribution of answers in
Figure~\ref{fig:JudgmentsK2} shows that small error counts occur at
many different steps, whereas we do see a concentrated rise in answers
at the critical position for local readings. Also, so far we have not
taken into account the sequential structure of our task. It might be
that local readings are infrequent because subjects tend to exit early
in the sequence, rather than late. Or it might be that our count for
local answers is exaggerated by a bias to answer later in the
sequence. This is why we need preference-related controls and a more
fine-grained analysis eventually.

\paragraph{Preference-related controls.} Positional answers for our
preference-related control conditions are shown in
Table~\ref{tab:count_data_TF}.\fn{We removed 19 data points for the
  \ec-conditions because of a coding mistake that presented subjects
  with incongruent sentence-picture pairs. Including these and
  classifying them as \emph{errors} does not change the qualitative
  results of the reported analyses.} Judgments were coded as \ec or as
\lc if they were as expected under one of these readings, and as
\emph{error} if they were not. As expected, most answers classify as
\lc-readings, fewer as \ec-readings. Moreover, intonation does seem to
have the expected effect as well: as compared to neutral intonation,
\lc-cueing intonation increases the count for \lc-readings, while
\ec-cueing increases the count for \ec-readings. If we compare the
number of \lc- or \ec-readings for each intonation type across
sequences, we see that there are always more answers indicative of the
relevant readings when that reading can be judged later in the
sequence. This suggests a general tendency to answer later in the
sequence, rather than at the earliest possible step.

\begin{table}
  \centering
  \begin{tabular}{lcccccccc@{\hskip 0.6cm}ccc}
    && \multicolumn{7}{c}{truth value at step}
    & \multicolumn{3}{c}{classification}
    \\ \cmidrule(l){3-9} \cmidrule(r){10-12}
    condition &
    & 1
    & 2
    & 3
    & 4
    & 5
    & 6
    & 7
    & \lc
    & \ec
    & err \\ \midrule
    \lc-ntr 
    & T & 0 & 0 & \textbf{87} & 1 & 0 & 9 & 0 
    & 87 & 32 & 13 \\
    & F & 0 & 0 & 3 & 0 & 0 & \textbf{32} & 0 \\
    \addlinespace[0.25cm]
    \lc-\lc-cue
    & T & 0 & 0 & \textbf{108} & 1 & 1 & 7 & 0 
    & 108 & 16 & 10 \\
    & F & 0 & 0 & 1 & 0 & 0 & \textbf{16} & 0 \\
    \addlinespace[0.25cm]
    \lc-\ec-cue
    & T & 0 & 0 & \textbf{51} & 4 & 0 & 7 & 0 
    & 51 & 59 & 25 \\
    & F & 2 & 1 & 7 & 0 & 0 & \textbf{59} & 1 \\
    \addlinespace[0.25cm]
    \ec-ntr
    & T & 0 & 0 & 0 & 0 & \textbf{92} & - & - 
    & 92 & 22 & 13 \\
    & F & 1 & 0 & \textbf{22} & 6 & 6 & - & - \\
    \addlinespace[0.25cm]
    \ec-\lc-cue
    & T & 0 & 0 & 0 & 0 & \textbf{112} & - & - 
    & 112 & 13 & 4 \\
    & F & 0 & 1 & \textbf{13} & 1 & 2 & - & - \\
    \addlinespace[0.25cm]
    \ec-\ec-cue
    & T & 0 & 0 & 0 & 0 & \textbf{65} & - & - 
    & 65 & 31 & 30 \\
    & F & 2 & 0 & \textbf{31} & 8 & 20 & - & - \\
    \addlinespace[0.25cm]

  \end{tabular}
  \caption{Observed truth-value judgments in preference-related controls.}
  \label{tab:count_data_TF}
\end{table}

% \begin{figure}[]
% \centering

%  \subfloat[][\LC-sequence]{

% \includegraphics[width=0.9\textwidth]{positional_answers_TF_LC.pdf}
% }

%  \subfloat[][\EC-sequence]{

% \includegraphics[width=0.9\textwidth]{positional_answers_TF_EC.pdf}
% }

% \caption{Answers for \lc-sequences and \ec-sequences. \emph{True}
%   judgements are plotted upwards for each step in the sequence,
%   \emph{false} judgements downwards.}
% \label{Fig:TF_judgments}
% \end{figure}

% \begin{table}[]
% \centering

% \begin{tabular}{lcccc}
%   condition & position & \multicolumn{3}{c}{response type} \\ \cmidrule(r){3-5}
%   && \emph{LC} & \emph{EC} & \emph{error}  \\
%   \midrule \addlinespace[0.15cm]
%   \textbf{\lc neutral} 
%   & Pos 1 & 27 &  7  & 4 \\
%   & Pos 2 & 23 &  11 & 4 \\
%   & Pos 3 & 26 &  9  & 3 \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{76} &  \textbf{27} & \textbf{11}  \\
%   \addlinespace[0.25cm]
%   \textbf{\lc with \lc cue} 
%   & Pos 1 & 26 &  7 & 5  \\
%   & Pos 2 & 31 &  5 & 2  \\
%   & Pos 3 & 33 &  3 & 2  \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{90} &  \textbf{15} & \textbf{9}  \\
%   \addlinespace[0.25cm]
%   \textbf{\lc with \ec cue} 
%   & Pos 1 & 14 &  17 & 7  \\
%   & Pos 2 & 15 &  16 & 7  \\
%   & Pos 3 & 15 &  17 & 6  \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{44} &  \textbf{50} & \textbf{20}  \\
%   \addlinespace[0.25cm]
%   \textbf{\ec neutral} 
%   & Pos 1 & 22 &  6 & 5  \\
%   & Pos 2 & 28 &  6 & 4  \\
%   & Pos 3 & 29 &  7 & 2  \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{79} &  \textbf{19} & \textbf{11}  \\
%   \addlinespace[0.25cm]
%   \textbf{\ec with \lc cue} 
%   & Pos 1 & 30 &  5 & 1  \\
%   & Pos 2 & 32 &  5 & 0  \\
%   & Pos 3 & 31 &  3 & 2  \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{93} &  \textbf{13} & \textbf{3}  \\
%   \addlinespace[0.25cm]
%   \textbf{\ec with \ec cue} 
%   & Pos 1 & 19 &  10 & 7  \\
%   & Pos 2 & 19 &  7  & 9  \\
%   & Pos 3 & 19 &  7  & 11  \\ \addlinespace[0.15cm]
%   & \textbf{Total} & \textbf{57} &  \textbf{24} & \textbf{27}  \\
% \end{tabular}

% \caption{Contingency table of classified responses for the
%   preference-related controls. As before, the factor position encodes
%   whether participants saw the condition in question for the first,
%   second or third time during the whole experiment.}
% \label{tab:CC-ContingencyTable-TF}
% \end{table}
